Let’s Disco – Publishing person-level data as Linked Data

### 2015-03-17 paper/ISWC 2015 Tutorial/ISWC-2015-tutorial.tex
Last changes

%
%
\title{Let’s Disco – Publishing person-level data as Linked Data.}
\subtitle{Building domain-specific Data Sets with Disco, PHDD, XKOS and widely used Vocabularies.
}
%
\titlerunning{XXXXX}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Benjamin Zapilko\inst{1} \and Thomas Bosch\inst{1} \and Joachim Wackerow\inst{1}}
%
\authorrunning{XXXXX} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\institute{GESIS – Leibniz Institute for the Social Sciences, Germany\\
\email{firstname.lastname}@gesis.org}

@@

\begin{abstract}
The DDI-RDF Discovery Vocabulary (Disco) is an RDF Schema vocabulary that enables the representation of person-level data sets and related metadata.
It is based on DDI (Data Documentation Initiative) which is a metadata standard related to the observation and measurement of human activity.
%Disco is intended to provide means to describe person-level data by essential metadata for the discovery purpose. 
%Using Disco, such data sets can be discovered in the Web of Linked Data by using RDF technologies, e.g. searching for specific questions, topics, and geographical coverage. 
Using Disco, such data sets which are often used in different domains like the social, ecomical and behavoural sciences can be published as Linked Data. 
However, for a meaningful and complete publication of these data sets, additional established RDF vocabularies (e.g. RDF Data Cube, DCAT, SKOS, PROV-O, XKOS, and PHDD) are reused to a large extend. 
This combination allows for expressing information on metadata of data collections, single data sets, relationships between them, different versions of them and related provenance information. 
In this tutorial, we show how Disco is interwoven with these vocabularies and how these connections can be used in order to publish complex and domain-specific data sets.
In different real world use cases, we demonstrate the adoption and inclusion of Disco in existing information systems. 
%Existing DDI instances are stored in form of XML documents which can be transformed into DDI-RDF and therefore exposed as Linked Data.
%Additionally, we present typical metadata constraints of DDI metadata as well as how to formulate them by different constraint languages (e.g. OWL 2) and how to actually validate them.

>>>>

%
%
\title{Let’s Disco – Publishing person-level data as Linked Data}
\subtitle{Building domain-specific Data Sets with Disco, PHDD, XKOS and widely used Vocabularies
}
%
\titlerunning{XXXXX}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Benjamin Zapilko\inst{1} \and Thomas Bosch\inst{1} \and Joachim Wackerow\inst{1}}
%
\authorrunning{XXXXX} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\institute{GESIS – Leibniz Institute for the Social Sciences, Germany\\
\email{firstname.lastname}@gesis.org}

@@

\begin{abstract}
The DDI-RDF Discovery Vocabulary (Disco) is an RDF Schema vocabulary that enables the representation of person-level data sets and related metadata.
It is based on DDI (Data Documentation Initiative) which is a metadata standard related to the observation and measurement of human activity.
Using Disco, such data sets which are often used in different domains like the social, ecomical and behavoural sciences can be published as Linked Data. 
However, for a meaningful and complete publication of these data sets, additional established RDF vocabularies (e.g. RDF Data Cube, DCAT, SKOS, PROV-O, XKOS, and PHDD) are reused to a large extend. 
This combination allows for expressing information on metadata of data collections, single data sets, relationships between them, different versions of them and related provenance information. 
In this tutorial, we show how Disco is interwoven with these vocabularies and how these connections can be used in order to publish complex and domain-specific data sets.
In different real world use cases, we demonstrate the adoption and inclusion of Disco in existing information systems. 
%Existing DDI instances are stored in form of XML documents which can be transformed into DDI-RDF and therefore exposed as Linked Data.
%Additionally, we present typical metadata constraints of DDI metadata as well as how to formulate them by different constraint languages (e.g. OWL 2) and how to actually validate them.
